%standard 6.1


%start_of_questions


%new_question
%%%%%%%%%%%%%%%%%%%%%
	% Problem 1
	% Difficulty: 1
%%%%%%%%%%%%%%%%%%%%%
	\item 
		Zyra the code mage has hidden a mysterious cipher in reversed messages. 
		You must help Zyra uncover the secrets of the digital realm. 
		Create a function called $reverse\_string$ that takes the variable $word$ 
		(a string) and returns the word in reversed order. \\
		For this problem, you must use iteration (a loop) not slicing.

	\textbf{Examples:}
		\begin{itemize}
			\item reverse\_string(\csq{programming}) $\rightarrow$ \csq{gnimmargorp}
			\item reverse\_string(\csq{python}) $\rightarrow$ \csq{nohtyp}
			\item reverse\_string(\csq{hello}) $\rightarrow$ \csq{olleh}
		\end{itemize}


%new_question
%%%%%%%%%%%%%%%%%%%%%
	% Problem 2
	% Difficulty: 1
%%%%%%%%%%%%%%%%%%%%%
	\item 
		The \textbf{normal human body temperature} is 98.6F in Fahrenheit and 37C in Celsuis. 
		Create a function that determines if the \textit{temp} is considered a fever(anove normal 
		body temperature) or not.
		\textit{temp} will be measured in Fahrenheit and Celsuis.\\
		Notice: The F or C will always be the last character in the string.

	\textbf{Examples:}
	\begin{itemize}
		\item is\_fever(\csq{99F}) $\rightarrow$ True, 
		\item is\_fever(\csq{37C}) $\rightarrow$ False, 
		\item is\_fever(\csq{98F}) $\rightarrow$ False, 
	\end{itemize}

%new_question
%%%%%%%%%%%%%%%%%%%%%
	% Problem 3
	% Difficulty: 1
%%%%%%%%%%%%%%%%%%%%%
	\item 
		%https://edabit.com/challenge/dBqLSk6qvudNdZrSx
		The \textbf{boiling point} of water is 212F in Fahrenheit and 100C in Celsuis. 
		Create a function that determines if the \textit{temp} is considered boiling or not.
		\textit{temp} will be measured in Fahrenheit and Celsuis.\\
		Notice: The F or C will always be the last character in the string.

	\textbf{Examples:}
	\begin{itemize}
		\item is\_boiling(\csq{212F}) $\rightarrow$ True, 
		\item is\_boiling(\csq{100C}) $\rightarrow$ True, 
		\item is\_boiling(\csq{0F}) $\rightarrow$ False, 
	\end{itemize}


%new_question
%%%%%%%%%%%%%%%%%%%%%
	% Problem 4
	% Difficulty: 1
%%%%%%%%%%%%%%%%%%%%%
	\item 
		%https://edabit.com/challenge/nfWirHJzNRBMAp9Df
		The \textbf{hamming distance} is the number of characters that differ between two strings.\\
		To illustrate, \\ \hspace*{1em}
		\begin{tabular}{lll}
			str1 = &\csq{abcbba}\\
			str2 = &\csq{abcbda}
		\end{tabular}\\
		The hamming distance is 1 since the only difference is the $5^{th}$ character. \\ 
		That is, \csq{b} in str1 vs. \csq{d} in str2.
		
		Your task: create a function named hamming distance that takes two strings as arguments, 
		and returns the hamming distance between the two strings.

	\textbf{Examples:}
		\begin{itemize}
			\item hamming\_distance(\csq{abcde}, \csq{bcdef}) $\rightarrow$ 5, 
				since all 5 letters are different.
			\item hamming\_distance(\csq{abcdef}, \csq{abcdef}) $\rightarrow$ 0, 
				since all 6 letters are the same.
			\item hamming\_distance(\csq{strong}, \csq{strung}) $\rightarrow$ 1,
				since there is only 1 character that is different.
		\end{itemize}

%new_question
%%%%%%%%%%%%%%%%%%%%%
	% Problem 5
	% Difficulty: 1
%%%%%%%%%%%%%%%%%%%%%
	\item 
		%https://edabit.com/challenge/vTGXrd5ntYRk3t6Ma
		An \textbf{Isogram} is a word that has no duplicate letters. Create a function that 
		takes a string and returns either True or False depending on whether or not it is 
		an \csq{isogram}. You may assume words will only have lower case letters.
		
	\textbf{Examples:}
		\begin{itemize}
			\item is\_isogram(\csq{algorithm}) $\rightarrow$ True
			\item is\_isogram(\csq{password}) $\rightarrow$ False (multiple of s)
			\item is\_isogram(\csq{consecutive}) $\rightarrow$ False (multiple of c)
			\item is\_isogram(\csq{python}) $\rightarrow$ True
		\end{itemize}

%new_question
%%%%%%%%%%%%%%%%%%%%%
	% Problem 6
	% Difficulty: 1
%%%%%%%%%%%%%%%%%%%%%
	\item 
		%https://edabit.com/challenge/Mv5qSgZKTLrLt9zzW
		A fruit juice company tags their fruit juices by concatenating the first 
		\textbf{three letters} of the words in a flavor's name, with its capacity. 
		Create a function that creates product IDs for different fruit juices.
		Notice that the first input is a string and the second is an integer.
		
	\textbf{Examples:}
		\begin{itemize}
			\item get\_drink\_ID(\csq{apple}, 500) $\rightarrow$ \csq{app500}
			\item get\_drink\_ID(\csq{pineapple}, 45) $\rightarrow$ \csq{pin45}
			\item get\_drink\_ID(\csq{watermelon}, 750) $\rightarrow$ \csq{wat750}
		\end{itemize}





%new_question
%%%%%%%%%%%%%%%%%%%%%
	% Problem 7
	% Difficulty: 1
%%%%%%%%%%%%%%%%%%%%%
	\item 
		Professor Dumbledore seeks to decipher powerful encoded spells in the Hogwarts Library, 
		their secrets revealed by the first letter of each word. Create a function called 
		$first\_letters$ that takes the variable $sentence$ (a string) and returns
		a string made up of the first letters of each word in the sentence. 

		\textbf{Examples:}
		\begin{itemize}
			\item first\_letters(\csq{wingardium leviosa makes objects float}) 
				$\rightarrow$ \csq{wlmof}
			\item first\_letters(\csq{expecto patronum repels dementors}) $\rightarrow$ \csq{eprd}
			\item first\_letters(\csq{the magic is within you}) $\rightarrow$ \csq{tmiwy}
		\end{itemize}

%new_question
%%%%%%%%%%%%%%%%%%%%%
	% Problem 8
	% Difficulty: 1
%%%%%%%%%%%%%%%%%%%%%
	\item 
		Severus Snape seeks to harness powerful spells in the Hogwarts Library, you must 
		encode them by using the last letter of each word. Create a function called 
		$last\_letters$ that takes the variable $sentence$ (a string) and returns
		a string made up of the last letters of each word in the sentence. 

		\textbf{Examples:}
		\begin{itemize}
			\item last\_letters(\csq{wingardium leviosa makes objects float}) 
				$\rightarrow$ \csq{masst}
			\item last\_letters(\csq{expecto patronum repels dementors}) $\rightarrow$ \csq{omss}
			\item last\_letters(\csq{the magic is within you}) $\rightarrow$ \csq{ecsnu}
		\end{itemize}



%new_question
%%%%%%%%%%%%%%%%%%%%%
	% Problem 9
	% Difficulty: 1
%%%%%%%%%%%%%%%%%%%%%
	\item
		Write a function called \textit{flip\_flop} that takes a string as an argument 
		and returns  a new word made up of the second half of the word first combined 
		with the first half of the word second.

		\textbf{Examples:}
		\begin{itemize}
			\item \textit{flip\_flop}(\csq{abcd}) $\rightarrow$ \csq{cdab} 
				(that is, \csq{cd} then \csq{ab} \dots even length)
			\item \textit{flip\_flop}(\csq{grapes}) $\rightarrow$ \csq{pesgra} 
				(that is, \csq{pes} then \csq{gra} \dots even length)
			\item \textit{flip\_flop}(\csq{abcde})$\rightarrow$ \csq{decab}
				(that is, \csq{de} then \csq{c} then \csq{ab} \dots odd length)
			\item \textit{flip\_flop}(\csq{cranberries})$\rightarrow$ \csq{rriesecranb}
				(that is, \csq{rries} then \csq{e} then \csq{cranb} \dots odd length)

		\end{itemize}

%end_of_questions
%make sure to leave at least one blank line below

