%standard 15.3


%start_of_questions



%%%%%%%%%%%%%%%%%%%%%
	% Problem 8
	% Difficulty: 3
%%%%%%%%%%%%%%%%%%%%%
%new_question
	\item 
		You are building a color picker feature for a drawing app.  
		The user selects a color by entering its position in a preset list of colors.\\

		A list contains some colors, shown below:
		\begin{itemize}
			\item \texttt{[\csq{red}, \csq{green}, \csq{blue}, \csq{yellow}, \csq{purple}]}
		\end{itemize}
		Write a \textbf{program} that asks the user to enter an \textbf{index} and then prints the 
		corresponding color. If the user enters an invalid index or input, they should be asked to 
		try again until a valid index is given.

		The program should handle the following errors:
		\begin{itemize}
			\item If the input is not a number (\textbf{ValueError}), 
				print \csq{Invalid input. Try again.}
			\item If the index is out of range (\textbf{IndexError}), 
				print \csq{Index out of range. Try again.}
		\end{itemize}

		\textbf{Examples:}
		\begin{itemize}
			\item \csq{Enter an index:} 2 $\rightarrow$ \csq{blue}
			\item \csq{Enter an index:} 10 $\rightarrow$ \csq{Index out of range. Try again.}
			\item \csq{Enter an index:} \csq{green} $\rightarrow$ \csq{Invalid input. Try again.}
			\item (after retry) \csq{Enter an index:} 1 $\rightarrow$ \csq{green}
		\end{itemize}

%Errors: IndexError, ValueError


%%%%%%%%%%%%%%%%%%%%%
	% Problem 9
	% Difficulty: 3
%%%%%%%%%%%%%%%%%%%%%
%new_question
	\item 
		You've been asked to help build part of a travel booking system.  
		One of the features lets users type in a country code (like \csq{US}) and shows them the 
		full country name to confirm their destination.

		A dictionary stores some country codes, shown below: 
			$$\texttt{\{\csq{US}:\csq{United States}, \csq{FR}:\csq{France}, 
				\csq{JP}:\csq{Japan}, \csq{BR}:\csq{Brazil}\}}$$
		Write a \textbf{program} that asks the user to enter a country code (like \csq{US}) 
		and then prints the full country name. If the user enters an invalid code, they should 
		be asked to try again until a valid code is entered.

		The program should handle the following errors:
		\begin{itemize}
			%\item If the input is empty, print \csq{Invalid input. Try again.}
			\item If the code is not found in the dictionary (\textbf{KeyError}), 
				print \csq{Code not found. Try again.}
		\end{itemize}

		\textbf{Examples:}
		\begin{itemize}
			\item \csq{Enter a country code:} \csq{JP} $\rightarrow$ \csq{Japan}
			\item \csq{Enter a country code:} \csq{XYZ} $\rightarrow$ 
				\csq{Code not found. Try again.}
			%\item \csq{Enter a country code:} \csq{} $\rightarrow$ \csq{Invalid input. Try again.}
			\item (after retry) \csq{Enter a country code:} \csq{BR} $\rightarrow$ \csq{Brazil}
		\end{itemize}

%Errors: KeyError, ValueError


%%%%%%%%%%%%%%%%%%%%%
	% Problem 10
	% Difficulty: 3
%%%%%%%%%%%%%%%%%%%%%
%new_question
	\item 
		A game show awards a cash prize to be split evenly among a group of winners.  
		Write a \textbf{program} that asks the user to:
		\begin{enumerate}
			\item Enter the prize amount in dollars
			\item Enter the number of winners
		\end{enumerate}

		The program should calculate how much each person gets by dividing the prize by the 
		number of winners.
		The program should keep asking until the input is valid, and handle the following errors:
		\begin{itemize}
			\item If the input is not a number (e.g. typing \csq{five}) (\textbf{ValueError}), 
				print \csq{Invalid input. Try again.}
			\item If there are no winners (\textbf{ZeroDivisionError}), 
				print \csq{Must have at least one winner. Try again.}
			%\item If the prize is so large that it causes an error, print \csq{Prize amount 
			%too large. Try a smaller amount.}
		\end{itemize}

		\textbf{Examples:}
		\begin{itemize}
			\item \csq{Enter prize amount:} 10000 \\
			      \csq{Enter number of winners:} 4 $\rightarrow$ 2500.0
			\item \csq{Enter number of winners:} 0 $\rightarrow$ 
				\csq{Cannot divide by zero. Try again.}
			\item \csq{Enter prize amount:} \csq{grand} $\rightarrow$ 
				\csq{Invalid input. Try again.}
			%\item \csq{Enter prize amount:} 100000000000000000000000 \\ \csq{Enter number of 
			%winners:} 1 $\rightarrow$ \csq{Prize amount too large. Try a smaller amount.}
		\end{itemize}

%Errors: ValueError, ZeroDivisionError, OverflowError





%end_of_questions
%make sure to leave at least one blank line below

