%standard 3.3


%start_of_questions

%new_question
%%%%%%%%%%%%%%%%%%%%%
	% Problem 4
	% Difficulty: 3
%%%%%%%%%%%%%%%%%%%%%
	\item  
		The table below show what your resting heart rate should be based on age and athleticism.  
		Write a program that asks the user their age and desired athleticism goal, and then outputs 
		what their resting heart rate should be.

		\begin{minipage}{.45\textwidth}
			\begin{tabular}{c|cc}
				& \multicolumn{2}{c}{Athleticism}\\
				Age & Above Average & Below Average \\ \hline
				20 -- 39 & 47 -- 72 & 73 -- 93\\
				40 -- 59 & 46 -- 71 & 72 -- 94\\
				60 -- 79 & 45 -- 70 & 71 -- 97 \\
			\end{tabular}
		\end{minipage}
		\begin{minipage}{.45\textwidth}
			\vspace*{1em}
			Your end output should look similar to this
			\fbox{\parbox{\textwidth}{ Enter your age: 45\\
			Enter your athleticism goal: Below Average\\
			Your resting heart rate should be between 72--94.}}
		\end{minipage}





%new_question
%%%%%%%%%%%%%%%%%%%%%
	% Problem 10
	% Difficulty: 3
%%%%%%%%%%%%%%%%%%%%%
	\item  
		The table below shows the maximum health of characters based on race and class for a new 
		video game I am creating.  Write a program that asks the user for the race and the class of 
		their character, and then sets the \textit{health\_points}	variable according to the table 
		below.
		\begin{flushright}
		\begin{tabular}{c|cc}
			& \multicolumn{2}{c}{Race}\\
			Class & Elf & Ogre \\ \hline
			Warrior & 150 & 200\\
			Bard & 75 & 100\\
			Wizard & 25 & 50 \\
		\end{tabular}
		\end{flushright}
		
		\vspace*{-6em}
		\textit{health\_points} = -1\\
		\#Your code here.
		\vspace*{3em}





%new_question
%%%%%%%%%%%%%%%%%%%%%
	% Problem 15
	% Difficulty: 3
%%%%%%%%%%%%%%%%%%%%%
	\item  
		The table below shows what time different age groups (by grade) can swim at the pool.  There 
		are two time options, morning and afternoon.  Write a program that asks the user their grade 
		and whether they'd like to go in the morning or afternoon, and outputs the time the pool is 
		available for them.

		\begin{minipage}{.45\textwidth}
		\begin{tabular}{c|cc}
						& \multicolumn{2}{c}{Pool times}\\
			Grade 		& Morning 	& Afternoon \\ \hline
			k, 1 -- 3 	& 9 AM 		& 1 PM\\
			4 -- 8 		& 10 AM 	& 2 PM\\
			9 -- 12 	& 11 AM 	& 3 PM \\
		\end{tabular}
		\end{minipage}
		%
		\begin{minipage}{.45\textwidth}
			\ \\
			Your end output should look similar to this
			%(if you were to actually run the code).

			\fbox{\parbox{\textwidth}{ Enter your grade: 5\\
			Enter Morning OR Afternoon: Morning\\
			The pool is open at 10 AM.}}
		\end{minipage}



%end_of_questions








